Financialisation of Commodity Markets \\\large{Co-movement Behind-the-Scenes}

### 2024-09-27 paper.tex
Deploying to gh-pages from @ bautheac/financialisation-co-movement@17d928f09a98f0737dd9464bd9d461c9a21907ca 🚀

By grouping together assets by shared attribute dynamics in common
portfolios, asset pricing techniques--and factor models in
particular--are well suited to study co-movement
\citep{fama_common_1993, carhart_persistence_1997, asness_devil_2013, fama_five_factor_2015, hou_digesting_2015, asness_fact_2015, frazzini_betting_2014, asness_quality_2019}.
Careful, theory-based, attribute selection further enables a refined
analysis of market fundamentals
\citep{schwartz_short_2000, miffre_momentum_2007, gorton_fundamentals_2012, cortazar_commodity_2013, yang_investment_2013, daskalaki_factors_2014, szymanowska_anatomy_2014, fernandez_skewness_2018, bakshi_understanding_2019, boons_basis_2019, sakkas_factor_2020}.
We therefore develop a futures-based asset pricing framework that
includes factors constructed using both theoretical and liquidity
considerations. Using the weekly price, open interest and market
position data described above we construct market portfolios of
individual commodity nearby futures as well as mimicking portfolios for
market, commercial hedging pressure, term structure and liquidity risk
factors in returns. While our market portfolios are long only
combinations of particular commodity sets, our other mimicking
portfolios for risk factors are constructed as combinations of two
sub-portfolios (legs), one held long, one held short, which respective
constituents are pooled on a weekly basis according to risk factor
specific criteria.\\
All portfolios are equally weighted and returns for the two-legged
factors are calculated as the difference between the average return for
constituents of the long leg and that for the constituents of the short.
i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\))
for period \(t\):

@@

We use a time series regression approach where individual commodity
weekly front futures contract returns are regressed on returns to the
mimicking portfolio for a particular risk factor with the corresponding
\(\beta\)s and \(R^{2}\)s averaged. For the long-short factors the
results are reported independently for models where the regressor is the
factor itself or one of its legs (results available upon request).

@@

We further define aggregate backwardation (\textbf{backwardation}) and
contango (\textbf{contango}) \textbf{CHP} regimes as, for a given
period, \textbf{CHP} levels below and above the period's median
respectively and, in contrast with \citep{hong_what_2012} who aggregate
across sub-sectors, our \textbf{CHP} construction draws on the full
cross-section of US-traded assets considered in the study.

@@

\begin{longtable}[t]{>{}l>{}l>{}r>{}r>{}r>{}r}

\caption{\label{tbl-stats-no-regimes}This table shows mean returns and
volatility (sd) for the twenty four individual US commodities and the
six GB metals considered in the study as well as for two equally
weighted portfolios formed from the US commodities and the GB metals
respectively across the four periods of interest (past: 1997-2003;
financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018).
Mean values significant at the 1\%, 5\% and 10\% level are marked with
***, ** and * respectively. The results are discussed in
Section~\ref{sec-results}.}
\textcolor{black}{\textbf{asset}} & \textcolor{black}{\textbf{estimate}} & \textcolor{black}{\textbf{past}} & \textcolor{black}{\textbf{financialisation}} & \textcolor{black}{\textbf{crisis}} & \textcolor{black}{\textbf{post-crisis}}\\
\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
\textbf{Corn-\#2 yellow (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
\textbf{Oats (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
\textbf{Soybean meal (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
\textbf{Soybean oil (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
\textbf{Soybeans (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\
\textbf{Wheat-SRW (XCBT)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{24.93\%}} & \textcolor[HTML]{4285f4}{\textbf{33.03\%}} & \textcolor[HTML]{4285f4}{\textbf{37.62\%}} & \textcolor[HTML]{4285f4}{\textbf{26.58\%}}\\
\textbf{\cellcolor{gray!10}{Cattle-feeder (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.87\%}}}\\
\textbf{Cattle-feeder (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{13.23\%}} & \textcolor[HTML]{4285f4}{\textbf{15.16\%}} & \textcolor[HTML]{4285f4}{\textbf{15.24\%}} & \textcolor[HTML]{4285f4}{\textbf{18.69\%}}\\
\textbf{\cellcolor{gray!10}{Cattle-live (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.92\%}}}\\
\textbf{Cattle-live (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.1\%}} & \textcolor[HTML]{4285f4}{\textbf{17.43\%}} & \textcolor[HTML]{4285f4}{\textbf{16.32\%}} & \textcolor[HTML]{4285f4}{\textbf{18.3\%}}\\
\textbf{\cellcolor{gray!10}{Lean hogs (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.73\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.09\%}}}\\
\textbf{Lean hogs (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.33\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{30.37\%}} & \textcolor[HTML]{4285f4}{\textbf{36.94\%}}\\
\textbf{\cellcolor{gray!10}{Cocoa (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.66\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.65\%}}}\\
\textbf{Cocoa (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.66\%}} & \textcolor[HTML]{4285f4}{\textbf{29.99\%}} & \textcolor[HTML]{4285f4}{\textbf{31.03\%}} & \textcolor[HTML]{4285f4}{\textbf{24.69\%}}\\
\textbf{\cellcolor{gray!10}{Coffee-C (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.2\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.99\%}}}\\
\textbf{Coffee-C (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{43.84\%}} & \textcolor[HTML]{4285f4}{\textbf{32.3\%}} & \textcolor[HTML]{4285f4}{\textbf{30.17\%}} & \textcolor[HTML]{4285f4}{\textbf{31.86\%}}\\
\textbf{\cellcolor{gray!10}{Cotton-\#2 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.24\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.53\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.5\%}}}\\
\textbf{Cotton-\#2 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{26.38\%}} & \textcolor[HTML]{4285f4}{\textbf{29.01\%}} & \textcolor[HTML]{4285f4}{\textbf{33.26\%}} & \textcolor[HTML]{4285f4}{\textbf{20.61\%}}\\
\textbf{\cellcolor{gray!10}{Lumber (XCME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.9\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.06\%}}}\\
\textbf{Lumber (XCME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{30.58\%}} & \textcolor[HTML]{4285f4}{\textbf{29.39\%}} & \textcolor[HTML]{4285f4}{\textbf{36.31\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
\textbf{\cellcolor{gray!10}{Orange juice (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.4\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.8\%}}}\\
\textbf{Orange juice (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}} & \textcolor[HTML]{4285f4}{\textbf{33.01\%}} & \textcolor[HTML]{4285f4}{\textbf{34.43\%}} & \textcolor[HTML]{4285f4}{\textbf{29.37\%}}\\
\textbf{\cellcolor{gray!10}{Sugar-\#11 (IFUS)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{24.87\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.16\%}}}\\
\textbf{Sugar-\#11 (IFUS)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{34.88\%}} & \textcolor[HTML]{4285f4}{\textbf{33.25\%}} & \textcolor[HTML]{4285f4}{\textbf{37.9\%}} & \textcolor[HTML]{4285f4}{\textbf{28.72\%}}\\
\textbf{\cellcolor{gray!10}{Natural gas (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.33\%}}}\\
\textbf{Natural gas (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{61.55\%}} & \textcolor[HTML]{4285f4}{\textbf{54.6\%}} & \textcolor[HTML]{4285f4}{\textbf{53.58\%}} & \textcolor[HTML]{4285f4}{\textbf{44.58\%}}\\
\textbf{\cellcolor{gray!10}{Crude oil-WTI (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.67\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.64\%}}}\\
\textbf{Crude oil-WTI (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{32.56\%}} & \textcolor[HTML]{4285f4}{\textbf{42.84\%}} & \textcolor[HTML]{4285f4}{\textbf{34.69\%}}\\
\textbf{\cellcolor{gray!10}{Gasoline (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.65\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{30.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.37\%}}}\\
\textbf{Gasoline (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{42.77\%}} & \textcolor[HTML]{4285f4}{\textbf{41.76\%}} & \textcolor[HTML]{4285f4}{\textbf{40.07\%}} & \textcolor[HTML]{4285f4}{\textbf{37.09\%}}\\
\textbf{\cellcolor{gray!10}{Heating oil (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.88\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.44\%}}}\\
\textbf{Heating oil (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{40.75\%}} & \textcolor[HTML]{4285f4}{\textbf{35.09\%}} & \textcolor[HTML]{4285f4}{\textbf{33.17\%}} & \textcolor[HTML]{4285f4}{\textbf{30.56\%}}\\
\textbf{\cellcolor{gray!10}{Copper (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*28.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.1\%}}}\\
\textbf{Copper (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.23\%}} & \textcolor[HTML]{4285f4}{\textbf{31.89\%}} & \textcolor[HTML]{4285f4}{\textbf{34.91\%}} & \textcolor[HTML]{4285f4}{\textbf{19.56\%}}\\
\textbf{\cellcolor{gray!10}{Gold (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.35\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.53\%}}}\\
\textbf{Gold (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.14\%}} & \textcolor[HTML]{4285f4}{\textbf{18.89\%}} & \textcolor[HTML]{4285f4}{\textbf{21.46\%}} & \textcolor[HTML]{4285f4}{\textbf{14.41\%}}\\
\textbf{\cellcolor{gray!10}{Palladium (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.03\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.75\%}}}\\
\textbf{Palladium (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{38.27\%}} & \textcolor[HTML]{4285f4}{\textbf{32.71\%}} & \textcolor[HTML]{4285f4}{\textbf{36.14\%}} & \textcolor[HTML]{4285f4}{\textbf{25.38\%}}\\
\textbf{\cellcolor{gray!10}{Platinum (XNYM)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.56\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.92\%}}}\\
\textbf{Platinum (XNYM)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22.62\%}} & \textcolor[HTML]{4285f4}{\textbf{22.66\%}} & \textcolor[HTML]{4285f4}{\textbf{25.53\%}} & \textcolor[HTML]{4285f4}{\textbf{19.48\%}}\\
\textbf{\cellcolor{gray!10}{Silver (XCEC)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.43\%}}}\\
\textbf{Silver (XCEC)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{22\%}} & \textcolor[HTML]{4285f4}{\textbf{33.92\%}} & \textcolor[HTML]{4285f4}{\textbf{39.87\%}} & \textcolor[HTML]{4285f4}{\textbf{24.35\%}}\\
\textbf{\cellcolor{gray!10}{Aluminium (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.78\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.58\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.15\%}}}\\
\textbf{Aluminium (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{17.6\%}} & \textcolor[HTML]{4285f4}{\textbf{26.41\%}} & \textcolor[HTML]{4285f4}{\textbf{26.48\%}} & \textcolor[HTML]{4285f4}{\textbf{18.56\%}}\\
\textbf{\cellcolor{gray!10}{Copper (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.45\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**28.59\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.03\%}}}\\
\textbf{Copper (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.25\%}} & \textcolor[HTML]{4285f4}{\textbf{31.09\%}} & \textcolor[HTML]{4285f4}{\textbf{34.27\%}} & \textcolor[HTML]{4285f4}{\textbf{18.92\%}}\\
\textbf{\cellcolor{gray!10}{Lead (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.83\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{28.99\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{10.74\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.07\%}}}\\
\textbf{Lead (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{19.64\%}} & \textcolor[HTML]{4285f4}{\textbf{41.74\%}} & \textcolor[HTML]{4285f4}{\textbf{41.05\%}} & \textcolor[HTML]{4285f4}{\textbf{23.26\%}}\\
\textbf{\cellcolor{gray!10}{Nickel-primary (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.31\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.5\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.31\%}}}\\
\textbf{Nickel-primary (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{32.26\%}} & \textcolor[HTML]{4285f4}{\textbf{44.27\%}} & \textcolor[HTML]{4285f4}{\textbf{41.45\%}} & \textcolor[HTML]{4285f4}{\textbf{28.98\%}}\\
\textbf{\cellcolor{gray!10}{Tin-refined (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*29.1\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.46\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.68\%}}}\\
\textbf{Tin-refined (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.38\%}} & \textcolor[HTML]{4285f4}{\textbf{31.71\%}} & \textcolor[HTML]{4285f4}{\textbf{35.61\%}} & \textcolor[HTML]{4285f4}{\textbf{18.79\%}}\\
\textbf{\cellcolor{gray!10}{Zinc (XLME)}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.13\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.07\%}}}\\
\textbf{Zinc (XLME)} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{21.73\%}} & \textcolor[HTML]{4285f4}{\textbf{38.77\%}} & \textcolor[HTML]{4285f4}{\textbf{36.17\%}} & \textcolor[HTML]{4285f4}{\textbf{23.25\%}}\\
\textbf{\cellcolor{gray!10}{US commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{**15.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{9.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.18\%}}}\\
\textbf{US commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{10\%}} & \textcolor[HTML]{4285f4}{\textbf{13.62\%}} & \textcolor[HTML]{4285f4}{\textbf{17.58\%}} & \textcolor[HTML]{4285f4}{\textbf{9.86\%}}\\
\textbf{\cellcolor{gray!10}{GB commodities}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.47\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*21.77\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.25\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.72\%}}}\\
\textbf{GB commodities} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{15.66\%}} & \textcolor[HTML]{4285f4}{\textbf{26.91\%}} & \textcolor[HTML]{4285f4}{\textbf{30.24\%}} & \textcolor[HTML]{4285f4}{\textbf{16.19\%}}\\

@@

>>>>

By grouping together assets by shared attribute dynamics in common
portfolios, asset pricing techniques--and factor models in
particular--are well suited to study co-movement
\citep{fama_common_1993, carhart_persistence_1997, asness_devil_2013, fama_five_factor_2015, hou_digesting_2015, asness_fact_2015, frazzini_betting_2014, asness_quality_2019}.
Careful, theory-based, attribute selection further enables a refined
analysis of market fundamentals
\citep{schwartz_short_2000, miffre_momentum_2007, gorton_fundamentals_2012, cortazar_commodity_2013, yang_investment_2013, daskalaki_factors_2014, szymanowska_anatomy_2014, fernandez_skewness_2018, bakshi_understanding_2019, boons_basis_2019, sakkas_factor_2020}.
We therefore develop a futures-based asset pricing framework that
includes factors constructed using both theoretical and liquidity
considerations. Using the weekly returns, open interest and market
position data described above we construct market portfolios of
individual commodity nearby futures as well as mimicking portfolios for
market, commercial hedging pressure, term structure and liquidity risk
factors in returns. While our market portfolios are long only
combinations of particular commodity sets, our other mimicking
portfolios for risk factors are constructed as combinations of two
sub-portfolios (legs), one held long, one held short, which respective
constituents are pooled on a weekly basis according to risk factor
specific criteria.\\
All portfolios are equally weighted and returns for the two-legged
factors are calculated as the difference between the average return for
constituents of the long leg and that for the constituents of the short.
i.e, return on the mimicking portfolio for risk factor \(i\) (\(f_{i}\))
for period \(t\):

@@

We use a time series regression approach where individual commodity
weekly front futures contract returns are regressed on returns to the
mimicking portfolio for a particular risk factor with the corresponding
\(\beta\)s and \(R^{2}\)s averaged. For the long-short factors the
\(\beta\)s and \(R^{2}\)s are computed for models where the regressor is
the factor itself as well as both its long and short legs independently
(results available upon request).

@@

We further define aggregate backwardation (\textbf{backwardation}) and
contango (\textbf{contango}) \textbf{CHP} regimes as, for a given
period, sub-periods with \textbf{CHP} levels below and above the
period's median respectively and, in contrast with
\citep{hong_what_2012} who aggregate across sub-sectors, our
\textbf{CHP} construction draws on the full cross-section of US-traded
assets considered in the study.

@@

@@

\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{sd} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
